
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../images/")
```


# My Perception of Data Scientists

My initial perception of data scientists is that they apply statistical knowledge and programming expertise to extract information from data and solve business problems. While I still believe that to be true, I found the data science process to be more complicated than I had imagined. I feel there is a lack of standard practice compared to some of the other statistical disciplines, which makes some of the tasks more difficult such as choosing the parameters or picking the best model. 


# Current Thoughts of R

Having used SAS for more than 5 years, I find R to be very flexible and easy to use. For data science, there are so many packages available that makes the workflow smooth and intuitive. Ggplot is very versatile and allows me to create different kinds of plots with flexible formatting. Also, Shiny apps provide a good way for users to interact with the data. I will continue to use R for my work and personal interests and apply what I have learned from this course.  


# What I am going to do Differently

We have done a lot of Exploratory Data Analysis (EDA) in this course, and it really makes sense to me to get more insight of the dataset before proceeding. I will be doing more EDA in the future when I receive data so I can better understand the data before performing core tasks such as model fitting. I can also see myself creating Shiny apps to allow myself and collaborators to explore and interact with different data. 




```{r, echo = TRUE, eval=FALSE}
# Run this part in the console to render the output
rmarkdown::render("_Rmd/2021-11-28-Final-Reflection.Rmd", 
          output_format = "github_document", 
          output_dir = "_posts/",
          output_options = list(html_preview = FALSE)
          )
```

