---
title: "Programming Background"
author: "Joey Chen"
date: "9/13/2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../images/")
```


```{r, include = FALSE, eval=FALSE}
rmarkdown::render("_Rmd/2021-9-13-Programming-Background.Rmd", 
          output_format = "github_document", 
          output_dir = "_posts/",
          output_options = list(html_preview = FALSE)
          )
```

## My Programming Background

I have had years of programming experience in SAS before I learned R. What I like about R is that it is very flexible. For example, you can easily store a column from a dataset as an object. In SAS, everything works in blocks, most of which are Data Steps, and you can't really store a column as an object. However, I like how SAS stores the data as SAS datasets. It is much easier to read compared to R and it allows me to visually check for any data anomalies. All in all, I consider R to be an easy language to learn and is more intuitive compared to SAS.


## Example R Markdown Output

```{r}
plot(iris)
```


